### **INSTRUCTIONS**

Please follow the steps one by one to run each functions:

1. Loading CSV file of Titanic Dataset into RStudio:
   ```{r}
   Titanic <- read.csv("D:/Important Files Study/Titanic Dataset work/Titanic.csv")
   ```
*!!Please note that the location of the file should be where you have kept your file after downloading from kaeggle into your drive.!!*

2. Inspection of Dataset:
   ```{r}
   #Datset vewing
   View(Titanic)
   #Displaying the first few rows of the Dataset
   head(Titanic)
   #Summary of the dataset
   summary(Titanic)
   ```
3. Checking missing values in columns:
   ```{r}
   colSums(is.na(Titanic))
   ```
4. Handling missing values using median:
   ```{r}
   Titanic$Age[is.na(Titanic$Age)] <- median(Titanic$Age, na.rm = TRUE)
   # view columns again
   colSums(is.na(Titanic))
   ```
   
5. Dropping 'Fare' column(it should be determined by correlation coefficient but it is not implemented.):
   ```{r}
   Titanic <- subset(Titanic, select = -c(Fare))
   #Viewing columns again
   colSums(is.na(Titanic))
   ```

6. Creating new feature named 'FamilySize' using the help of 'SibSp' and 'Parch' columns:
   ```{r}
   Titanic$FamilySize <- Titanic$SibSp + Titanic$Parch + 1
   # view columns again
   colSums(is.na(Titanic))
   ```
   
7. Using one-hot encoding technique to convert categorical 'Sex' and 'Embarked' columns into numerical variables and then remove the original columns:
   ```{r, message=FALSE, warning=FALSE}
   library(caret)
   Titanic <- cbind(Titanic, model.matrix(~ Sex + Embarked, Titanic))
   Titanic <- subset(Titanic, select = -c(Sex, Embarked))
   ```
  *!!DO PLEASE INSTALL THIS CARET PACKAGE BEFORE RUNNING ONE-HOT ENCODING!!*

  
8. Splitting Dataset for train and test:
   ```{r}
     library(caret)
  
  #Setting seed 40 for reproductibility
  set.seed(40)
  
  #Splitting Dataset for training and testing(85% for training and 15% for testing but you cant determine by yourself. It is better to always take more data for training purpose than testing)
  inTrain <- createDataPartition(Titanic$Survived, p = 0.85, list = FALSE)
  
  train <- Titanic[inTrain, ]
  
  test <- Titanic[-inTrain, ]
   ```
  
   
   